%%% Template created by Marcel Neunhoeffer & Sebastian Sternberg
%%%This is a more detailed protocol adapted from the one found in the Zymo Research Direct-zol RNA MiniPrep Kit


% This defines the style 
\documentclass[a4paper,12pt]{article} 

% Sets the margins 
\usepackage[top = 2.5cm, bottom = 2.5cm, left = 2.5cm, right = 2.5cm]{geometry} 

% Unfortunately, LaTeX has a hard time interpreting German Umlaute. The following two lines and packages should help
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% The default setting of LaTeX is to indent new paragraphs
\usepackage{setspace}
\setlength{\parindent}{0in}

% The fancyhdr package let's us create nice headers
\usepackage{fancyhdr}

%This package helps with SI units
\usepackage{siunitx}

% With this command we can customize the header style
\pagestyle{fancy} 

% This makes sure we do not have other information in our header or footer
\fancyhf{} 

% \lhead puts text in the top left corner. \footnotesize sets our font to a smaller size
\lhead{\footnotesize RNA Extraction Protocol}

% We want to put our page number in the center
\cfoot{\footnotesize \thepage} 



\begin{document}

% This command disables the header on the first page
\thispagestyle{empty} 

\begin{tabular}{p{15.5cm}} % This is a simple tabular environment to align your text nicely 
{\large \bf RNA Extraction Protocol} \\
Matute Lab \\ Written By: David Peede  \\ Last Update: August 2020\\
\hline % \hline produces horizontal lines
\\
\end{tabular} % Our tabular environment ends here

\vspace*{0.3cm} % Now we want to add some vertical space in between the line and our title

\begin{tabular}{p{15.5cm}} % Everything within the center environment is centered
	{\Large Materials Needed:} 
	\vspace{2mm}
	{Zymo Research Direct-zol RNA MiniPrep Kit} \\ {RNaseZAP}\\ {TRIZOL} \\ {95-100\% Ethanol} \\ {RNase and DNase-free \SI{1.5}{\milli\liter} Tubes} \\ {RNase and DNase-free Pipette Tips}
		
\end{tabular}

\vspace{0.4cm}

\textbf{IMPORTANT NOTE}: RNase lives on our skin to protect us from RNA viruses, so be careful not to contaminate your samples and if at any point during this protocol you need to touch something (e.g. the Zymo kit, pipettes, reagents, pens, gloves, and/or centrifuge for example) make sure to wipe it down with RNaseZAP beforehand. 

\begin{enumerate}

\item Create a sterile workplace by cleaning off your bench space with 70\% EtOH, followed by RNaseZAP.
\item With gloves on wash one pestle per sample first with soap and water, then with 70\% EtOH, and finally with RNaseZAP; after the pestles are appropriately cleaned place them on your sterile workplace.
\item Add \SI{400}{\micro\liter} of TRIZOL to each \SI{1.5}{\milli\liter} tube containing 20-50 frozen \textit{Drosopohila/Aedes} or add \SI{200}{\micro\liter} of TRIZOL to each \SI{1.5}{\milli\liter} tube containing 1-19 frozen \textit{Drosopohila/Aedes} and then homogenize the flies using a clean pestle treated with RNaseZAP until you can no longer recognize any fly parts.  
\item Add an equal volume to the amount of TRIZOL added of 95-100\% EtOH and mix thoroughly by pipetting.
\item Pipette the mixture into a Zymo-Spin Column in a collection tube, centrifuge at 16,000 x g for 30 seconds, transfer the Zymo-Spin Column into a new collection tube and discard the flow-through. 
\item Add \SI{400}{\micro\liter} of RNA Wash Buffer to the  Zymo-Spin Column and centrifuge at 16,000 x g for 30 seconds.
\item In a new RNase-free \SI{1.5}{\milli\liter} tube add \SI{5}{\micro\liter} of DNase 1,  \SI{75}{\micro\liter} of DNA Digestion Buffer, mix gently by inverting the tube, and add the mixture directly onto the column matrix. 
\item Incubate at room temperature for 15 minutes before proceeding to step 9.
\item Add \SI{400}{\micro\liter} of Direct-zol RNA PreWash to the Zymo-Spin Column and centrifuge at 16,000 x g for 30 seconds then discard the flow-through.
\item Repeat step 9.
\item Add \SI{700}{\micro\liter} of RNA Wash Buffer to the Zymo-Spin Column, centrifuge at 16,000 x g for 1 minute, and carefully transfer the Zymo-Spin Column into a  new RNase-free \SI{1.5}{\milli\liter} tube.
\item To elute the RNA from the Zymo-Spin Column add \SI{50}{\micro\liter} of RNase and DNase-free water directly onto the column matrix and centrifuge at 16,000 x g for 30 seconds.
\item Store the eluted RNA in the -80. 
\end{enumerate}



\end{document}
